### 2020-12-18 02_background.tex
changes

%Related efforts:
%
%\begin{itemize}
%\item multi-robot planning and coordination
%\item manipulation task planning in general
%\item rearrangement 
%\item combinatorial literature
%\end{itemize}
The current work dealing with dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work. It is closely related to multi-robot planning and coordination where a challenge is the high dimensionality of the configuration space. %Early work has suggested to slightly reduce the~\cite{aronov1999motion} tried dimensionality reduction strategies. 
Optimal strategies were developed for simpler instances of the problem~\cite{SolYuZamHal15}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}. Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple}. General multi-robot planning tries to plan for multiple high-dimensional platforms \cite{wagner2012probabilistic,Gharbi:2009fu} using sampling-based techniques. 
Recent advances provide scalable~\cite{SoloveySH16:ijrr} and asymptotically optimal~\cite{Dobson:2017aa,Shome2019} sampling based frameworks. 
%Assembly planning \cite{halperin2000general,sundaram2001disassembly} is another related problem dealing with multi-body planning.

@@

%\textbf{The Traveling Salesman Problem}:
In this work we leverage a connection between dual-arm rearrangement and two combinatorial problems: (1) optimal matching~\cite{edmonds1965maximum} and (2) TSP. On the surface the problem seems closely related to multi-agent TSP.
%This can itself be tweaked with assumptions on same or different start and goal positions, symmetric or asymmetric metrics, directed or undirected graphs or posing the problem as an optimization
%A seminal paper~\cite{frederickson1976approximation} provides the formulation for k-TSP, with solutions that split a single tour.
%Prior work \cite{rathinam2006matroid} has formulated the problem of multi-start to multi-goal k-TSP as an optimization task. 
Prior work has formulated the k-TSP solution in terms of splitting a single tour~\cite{frederickson1976approximation} or as an optimization task~\cite{rathinam2006matroid}.
Some work~\cite{friggstad2013multiple} deals with asymmetric edge weights which are more relevant to the problems of our interest. 
%\textbf{Errand Scheduling}:
%If the object transfer is seen as an errand \cite{slavik1997errand} then a graph constructed with nodes being object-arm assignments and edges implying the order of coordinated execution. 
%There has been prior work \cite{garg2000polylogarithmic} that operates over the assignment graph(where pairwise assignments are nodes), an object's group consists of sets of nodes that include an object
The problem can be posed as an instance of multi vehicle pickup and delivery (PDP)~\cite{parragh2008survey}. 
%Most of the work has been motivated by ride-sharing applications and timed task scheduling, so there are a lot of variations that deal with time windows but this line of research provides some ILP formulations for the problem.
Prior work~\cite{coltin2014multi} has applied the PDP problem to robots, taking into account time windows and robot-robot transfers.
The seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has explored its complexity, and concedes to the hardness of the problem, while others studied cost bounds~\cite{TrePavFra13}, and proposed ILP formulations~\cite{savelsbergh1995general}. 
%The existing work that delves into the combinatorial challenges of the problem, do not account for the costs incurred due to coordination of the agents during task execution. 
%Pickup and Delivery problems under track contention \cite{caricato2003parallel}, makes an attempt to reason about the coordination of the robots over solutions obtained with Tabu Search.
Typically this line of work ignores coordination costs, though some methods~\cite{caricato2003parallel} reason about it on candidate solutions.

@@

\commentadd{
General task planning methods are unaware of the underlying structure studied in this work. Single-arm rearrangement solutions will also not be effective in this setting. The current work tries to bridge this gap and provide insights regarding the structure of dual-arm rearrangement. Under assumptions that enable this study, an efficient solution emerges for this problem.
}

>>>>

%Related efforts:
%
%\begin{itemize}
%\item multi-robot planning and coordination
%\item manipulation task planning in general
%\item rearrangement 
%\item combinatorial literature
%\end{itemize}
The current work dealing with \dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work. It is closely related to multi-robot planning and coordination where a challenge is the high dimensionality of the configuration space. %Early work has suggested to slightly reduce the~\cite{aronov1999motion} tried dimensionality reduction strategies. 
Optimal strategies were developed for simpler instances of the problem~\cite{SolYuZamHal15}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}. Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple}. General multi-robot planning tries to plan for multiple high-dimensional platforms \cite{wagner2012probabilistic,Gharbi:2009fu} using sampling-based techniques. 
Recent advances provide scalable~\cite{SoloveySH16:ijrr} and asymptotically optimal~\cite{Dobson:2017aa,Shome2019} sampling based frameworks. 
%Assembly planning \cite{halperin2000general,sundaram2001disassembly} is another related problem dealing with multi-body planning.

@@

%\textbf{The Traveling Salesman Problem}:
In this work we leverage a connection between \dual-arm rearrangement and two combinatorial problems: (1) optimal matching~\cite{edmonds1965maximum} and (2) TSP. On the surface the problem seems closely related to multi-agent TSP.
%This can itself be tweaked with assumptions on same or different start and goal positions, symmetric or asymmetric metrics, directed or undirected graphs or posing the problem as an optimization
%A seminal paper~\cite{frederickson1976approximation} provides the formulation for k-TSP, with solutions that split a single tour.
%Prior work \cite{rathinam2006matroid} has formulated the problem of multi-start to multi-goal k-TSP as an optimization task. 
Prior work has formulated the k-TSP solution in terms of splitting a single tour~\cite{frederickson1976approximation} or as an optimization task~\cite{rathinam2006matroid}.
Some work~\cite{friggstad2013multiple} deals with asymmetric edge weights which are more relevant to the problems of our interest. 
%\textbf{Errand Scheduling}:
%If the object transfer is seen as an errand \cite{slavik1997errand} then a graph constructed with nodes being object-arm assignments and edges implying the order of coordinated execution. 
%There has been prior work \cite{garg2000polylogarithmic} that operates over the assignment graph(where pairwise assignments are nodes), an object's group consists of sets of nodes that include an object
The problem can be posed as an instance of multi vehicle pickup and delivery (PDP)~\cite{parragh2008survey}. 
%Most of the work has been motivated by ride-sharing applications and timed task scheduling, so there are a lot of variations that deal with time windows but this line of research provides some ILP formulations for the problem.
Prior work~\cite{coltin2014multi} has applied the PDP problem to robots, taking into account time windows and robot-robot transfers.
The seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has explored its complexity, and concedes to the hardness of the problem, while others studied cost bounds~\cite{TrePavFra13}, and proposed ILP formulations~\cite{savelsbergh1995general}. 
%The existing work that delves into the combinatorial challenges of the problem, do not account for the costs incurred due to coordination of the agents during task execution. 
%Pickup and Delivery problems under track contention \cite{caricato2003parallel}, makes an attempt to reason about the coordination of the robots over solutions obtained with Tabu Search.
Typically this line of work ignores coordination costs, though some methods~\cite{caricato2003parallel} reason about it on candidate solutions.

@@

\commentadd{
General task planning methods are unaware of the underlying structure studied in this work. Single-arm rearrangement solutions will also not be effective in this setting. The current work tries to bridge this gap and provide insights regarding the structure of \dual-arm rearrangement. Under assumptions that enable this study, an efficient solution emerges for this problem.
}

### 2020-12-18 03_problem.tex
changes

Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  which can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$. The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where Every rearrangement $\arrangement \in \Aspace$ is an $n$-tuple $(\pose_1, \ldots, \pose_n)$. In valid arrangements $ \Afree \subset \Aspace$, the objects are pairwise disjoint.

@@

\begin{figure}[h]
    % \vspace{-.3in}
	\centering
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    % \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    % \vspace{-.35in}
\end{figure}
Two robot arms $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process. Let the set of collisions induced between the geometries of both the arms at two configurations along the path (at $t$) be denoted by the expression $ \pi^1(t) \ominus \pi^2(t) $. If there are no collisions then $\pi^1(t) \ominus \pi^2(t) = \emptyset$.
% Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. 
The space of dual-arm paths $\mathcal{D}$ is made of pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

% \vspace{-.1in}
{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which optimizes a cost function, and solution paths belong to the valid configuration space.

% \vspace{-.15in} 
% \begin{equation}
%  D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
% \label{eq:dualarm_constraint}
% \end{equation}
%  and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}

% \begin{align*}
%  D^* =  (\pi^{*1}, \pi^{*2}) = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
%  \ \textrm{such that} \ \arrangement(\ainit, D^*) = \atarget \textrm{ and,}\\ \pi^{*1} \in \cfree^1(\pi^{*2}), \pi^{*2} \in \cfree^2(\pi^{*1})  
% \end{align*}
%  and optimizes a cost function: $D^* =  .$}
\vspace{-0.1in}
\begin{align*}
 D^* =  (\pi^{*1}, \pi^{*2}) &= \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
 \ \textrm{such that} \ \arrangement(\ainit, D^*) &= \atarget \textrm{ ,and }\ \forall t\in[0,1]\\
 \pi^{*1}(t) \in \cfree^1,\ \pi^{*2}(t) \in \cfree^2,\ & \pi^{*1}(t) \ominus \pi^{*2}(t) = \emptyset
\end{align*}

@@

\commentadd{
\noindent \textbf{Note on Assumptions:} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications. The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}. A monotone solution also implies that every object's start and target is reachable by at least one arm. 
\cameraready{
Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable. Section~\ref{sec:integration} discusses a {\tt NO\_ACT} task that can deal with unbalanced object assignments between two arms. 
}

@@

>>>>

Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  which can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$. The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where every rearrangement $\arrangement \in \Aspace$ is an $n$-tuple $(\pose_1, \ldots, \pose_n)$. In valid arrangements $ \Afree \subset \Aspace$, the objects are pairwise disjoint.

@@

\begin{figure}[h]
    % \vspace{-.3in}
	\centering
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    % \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    % \vspace{-.35in}
\end{figure}
Two robot arms \footnote{We shall use superscripts to denote arms, and subscripts to index into some sequence or data-structure dependent on context, unless stated otherwise.} $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process. Let the set of collisions induced between the geometries of both the arms at two configurations along the path (at $t$) be denoted by the expression $ \pi^1(t) \ominus \pi^2(t) $. If there are no collisions then $\pi^1(t) \ominus \pi^2(t) = \emptyset$.
% Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. 
The space of dual-arm paths $\mathcal{D}$ is made of pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

% \vspace{-.1in}
{\definition [Optimal \Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which optimizes a cost function, and solution paths belong to the valid configuration space.
\begin{align*}
 D^* =  (\pi^{*1}, \pi^{*2}) &= \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
 \ \textrm{such that} \ \arrangement(\ainit, D^*) &= \atarget \textrm{ ,and }\ \forall t\in[0,1]\\
 \pi^{*1}(t) \in \cfree^1,\ \pi^{*2}(t) \in \cfree^2,\ & \pi^{*1}(t) \ominus \pi^{*2}(t) = \emptyset
\end{align*}

@@

\commentadd{
\subsection{Discussion on Assumptions} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications. The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}. A monotone solution also implies that every object's start and target is reachable by at least one arm.\cameraready{Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable. Section~\ref{sec:integration} discusses a {\tt NO\_ACT} task that can deal with unbalanced object assignments between two arms. 
}

@@

\revisions{
	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, involving their rearrangement to a disjoint target region or container. Such automation applications also create semi-structured workspaces that guarantee that all objects of interest are easily graspable (top-down for planar surfaces). This class of problems is monotone since the source and target poses are disjoint, and \textit{no transfer will require an intermediate location}. In this case object non-interactivity essentially implies that the workspace is well-behaved enough to allow feasible single-arm motion plans between top-down reachable poses of the object. The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same.

	The assumptions on the domain laid out in this work serve to identify the class of problems where our theoretical bounds will be close to the attained performance. \textit{The lazy variant proposed in this work is assured to iterate over all possible orderings of object-to-arm assignments, and take into account planning feasibility of the same. As such it is guaranteed to discover a solution as long as the \dual-arm rearrangement problem is monotone.} Admittedly, in domains where these assumptions are pathologically violated the theoretical and practical gains highlighted in this work will be compromised. The proposed method has limiting applicability to some interesting domains where objects are occluded, overlap, or lie in unstructured piles. Any non-monotonicity, i.e. problems that necessitate using an intermediate location, cannot be addressed by the current pipeline. These include puzzle-like or highly cluttered scenarios. 
}

### 2020-12-18 04_baseline.tex
changes

Mixed Integer Linear Programming (\milp) formulations can utilize highly optimized solvers \cite{gurobi}. Prior work has applied these techniques for solving m-TSP \cite{rathinam2006matroid,friggstad2013multiple} and pickup-and-delivery problems \cite{coltin2014multi,savelsbergh1995general}, but viewed these problems in a decoupled manner. This work outlines an \milp formulation for the synchronized dual-arm rearrangement problem that reasons about coordination costs arising from arm interactions in a shared workspace.

>>>>

Mixed Integer Linear Programming (\milp) formulations can utilize highly optimized solvers \cite{gurobi}. Prior work has applied these techniques for solving m-TSP \cite{rathinam2006matroid,friggstad2013multiple} and pickup-and-delivery problems \cite{coltin2014multi,savelsbergh1995general}, but viewed these problems in a decoupled manner. This work outlines an \milp formulation for the synchronized \dual-arm rearrangement problem that reasons about coordination costs arising from arm interactions in a shared workspace.

### 2020-12-18 05_approximation.tex
changes

\subsection{Importance of Transfers} In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
Lemma~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
may not be a meaningful bound on the performance ratio between a $k$-arm 
solution and a single-arm solution. This motivates the examination of another
often used setting---randomly chosen non-overlapping 
start and goal locations for $n$ objects (within a unit square). In order to derive a 
meaningful bound on the benefit of using a $2$-arm solution 
to a single-arm solution, we first derive a conservative cost of a single-arm solution. 
A single-arm optimal cost has three main parts: 1) the portion of the transfer cost involving the pickup and 
drop-off of the $n$ objects with a cost of $C_{pd} = nc_{pd}$, 2) the remaining transfer cost from 
start to goal for all objects $C_{sg}$, and 3) the transit cost 
going from the goals to starts $C_{gs}$. The single arm cost is  
%\vspace{-0.1in}
\begin{equation}
\label{eq:single-cost-exp}
C_{\rm single} = nc_{pd} + C_{sg} + C_{gs}.
%\vspace{-0.1in}
\end{equation}
To estimate Eq.~\ref{eq:single-cost-exp}, first note that the randomized setup 
will allow us to obtain the expected $C_{sg}$\cite{santalo2004integral} as
$\frac{2 + \sqrt{2} + 5\ln(1+\sqrt{2})}{15}nc_t \approx 0.52nc_t$.
Approximate $C_{gs}$ by simply computing an optimal assignment of the 
goals to the starts of the objects excluding the matching of the same start 
and goal. Denoting the distance cost of this matching as $C_{gs}^M$, clearly
$C_{gs} > C_{gs}^M$ because the paths produced by the matching may form 
multiple closed loops instead of the desired single loop that connects all 
starts and goals. However, the number of loops produced by the matching 
procedure is on the order of $\ln n$ and therefore, $C_{gs} < C_{gs}^M + 
c_t\ln n$, by~\cite{TrePavFra13}. By \cite{AjtKomTus84}, 
$C_{gs}^M = \Theta(\sqrt{n\ln n})$. Putting these together, we have,

@@

\begin{figure*}
%\vspace{-0.15in}
% \begin{figure}[H]
	\begin{center}
% 		\includegraphics[width=2.5in]{figures/mapp}
%		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
		\includegraphics[width=0.8\textwidth]{figures/algo_1}
		\includegraphics[width=0.8\textwidth]{figures/algo_2}
	\end{center}
%\vspace{-0.2in}
	\caption{ \tase{ \textit{(Top-left)} A dual-arm rearrangement problem. \textit{(Top-middle)} Directed edges between objects represents the assignment of arms to object \textit{transfers}. \textit{(Top-right)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}. \textit{(Bottom-left)} The legends for the different symbols used in the diagrams. \textit{(Bottom-middle)} A directed edge between object pairs represents the \textit{transit} between the target poses of the previous objects to the initial poses of the next. \textit{(Bottom-right)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments. A sequence of object-arm assignments form an optimal tour over a \textit{transit} graph.} }
%	\vspace{-0.2in}
	\label{fig:edge_matching}
% \end{figure}
\vspace{-0.1in}
\end{figure*}

@@

By Eq.~\ref{eq:cost_function}, the cost of the transfers can be reasoned about independent of their order. 
Define $\scomaset$ as the unordered set of $\coma\in\scoma$, then unordered transfer cost component corresponds to $\sum_{\coma\in\scomaset}\cost(T(\coma))$.
% We defined $ \scoma $ to be an ordered sequence of object-to-arm assignments. Let $ \scoma $ be a candidate solution to the synchronized dual-arm rearrangement problem. $ \scoma $ is an ordered sequence of $ \coma $, and $ \scomaset $ denote the unordered set of all $ \coma $ that comprise $ \scoma $. 
Since $ \graph $ is a complete graph (shown in Fig~\ref{fig:edge_matching}(top-right)) where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$. A candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once. In terms of the graph, this means that in the subset of edges $ \scomaset $ every vertex appears in only one edge. We arrive at the following crucial observation.

@@

A complete candidate solution to the problem now requires the sequence of~$ \coma $, 
%By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. 
which is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
%\vspace{-0.1in}
{
\lemma [Tour]
Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous dual-arm rearrangement problem.
}

>>>>

\subsection{Importance of Transfers} In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
Observation~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
may not be a meaningful bound on the performance ratio between a $k$-arm 
solution and a single-arm solution. This motivates the examination of another
often used setting---randomly chosen non-overlapping 
start and goal locations for $n$ objects (within a unit square). In order to derive a 
meaningful bound on the benefit of using a $2$-arm solution 
to a single-arm solution, we first derive a conservative cost of a single-arm solution. 
A single-arm optimal cost has three main parts: 1) the portion of the transfer cost involving the pickup and 
drop-off of the $n$ objects with a cost of $C_{pd} = nc_{pd}$, 2) the remaining transfer cost from 
start to goal for all objects $C_{sg}$, and 3) the transit cost 
going from the goals to starts $C_{gs}$. The single arm cost is  
%\vspace{-0.1in}
\begin{equation}
\label{eq:single-cost-exp}
C_{\rm single} = nc_{pd} + C_{sg} + C_{gs}.
%\vspace{-0.1in}
\end{equation}
To estimate Eq.~\ref{eq:single-cost-exp}, first note that the randomized setup 
will allow us to obtain the expected $C_{sg}$\cite{santalo2004integral} as
$\frac{2 + \sqrt{2} + 5\ln(1+\sqrt{2})}{15}nc_t \approx 0.52nc_t$.
Approximate $C_{gs}$ by simply computing an optimal assignment of the 
goals to the starts of the objects excluding the matching of the same start 
and goal. Denoting the distance cost of this matching as $C_{gs}^M$, clearly
$C_{gs} > C_{gs}^M$ because the paths produced by the matching may form 
multiple closed loops instead of the desired single loop that connects all 
starts and goals. However, the number of loops produced by the matching 
procedure is on the order of $\ln n$ and therefore, $C_{gs} < C_{gs}^M + 
c_t\ln n$, by~\cite{TrePavFra13}. By \cite{AjtKomTus84}, 
$C_{gs}^M = \Theta(\sqrt{n\ln n})$. Putting these together, we have,

@@

\begin{figure*}
%\vspace{-0.15in}
% \begin{figure}[H]
	\begin{center}
% 		\includegraphics[width=2.5in]{figures/mapp}
%		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
		\includegraphics[width=0.8\textwidth]{figures/algo_1}
		\includegraphics[width=0.8\textwidth]{figures/algo_2}
	\end{center}
%\vspace{-0.2in}
	\caption{ \tase{ \textit{(Top-left)} A \dual-arm rearrangement problem. \textit{(Top-middle)} Directed edges between objects represents the assignment of arms to object \textit{transfers}. \textit{(Top-right)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}. \textit{(Bottom-left)} The legends for the different symbols used in the diagrams. \textit{(Bottom-middle)} A directed edge between object pairs represents the \textit{transit} between the target poses of the previous objects to the initial poses of the next. \textit{(Bottom-right)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments. A sequence of object-arm assignments form an optimal tour over a \textit{transit} graph.} }
%	\vspace{-0.2in}
	\label{fig:edge_matching}
% \end{figure}
\vspace{-0.1in}
\end{figure*}

@@

By Eq.~\ref{eq:cost_function}, the cost of the transfers can be reasoned about independent of their order. 
Define $\scomaset$ as the unordered set of $\coma\in\scoma$, then unordered transfer cost component corresponds to $\sum_{\coma\in\scomaset}\cost(T(\coma))$.
% We defined $ \scoma $ to be an ordered sequence of object-to-arm assignments. Let $ \scoma $ be a candidate solution to the synchronized dual-arm rearrangement problem. $ \scoma $ is an ordered sequence of $ \coma $, and $ \scomaset $ denote the unordered set of all $ \coma $ that comprise $ \scoma $. 
Since $ \graph $ is a complete graph (shown in Fig~\ref{fig:edge_matching}(top-right)) where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$. A candidate solution of a monotone \dual-arm rearrangement problem must transfer every object exactly once. In terms of the graph, this means that in the subset of edges $ \scomaset $ every vertex appears in only one edge. We arrive at the following crucial observation.

@@

A complete candidate solution to the problem now requires the sequence of~$ \coma $, 
%By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. 
which is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
%\vspace{-0.1in}
{
\lemma [Tour]
Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous \dual-arm rearrangement problem.
}

### 2020-12-18 07_cost_bounds.tex
changes

\textit{Proof: }
From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
solution that is collision-free. Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors. The main overhead is then the potential collision between the two (disc) arms during transfer and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
with, an arm may travel a path formed by $n + 1$ straight line 
segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
two end-effector trajectories where potential collisions may happen. Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle. For each intersection, let one 
arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.

>>>>

\textit{Proof: }
From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
solution that is collision-free. Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors. The main overhead is then the potential collision between the two (disc) arms during transfer and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
with, an arm may travel a path formed by $n + 1$ straight line 
segments. 
\commentdel{Therefore, there are up to $(n + 1)^2$ intersections between the 
two end-effector trajectories where potential collisions may happen. Nevertheless,} 
Since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle. For each intersection, let one 
arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.

### 2020-12-18 08_evaluation.tex
changes

@@

\subsection{General Dexterous Manipulator} The second benchmark sets up two \kuka arms across a table with objects on it. The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose. Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates. 
% The lazy iterative variants show the robust scalability. 
Random split performs the worst since it is unlikely to chance upon valid motion plans. Single shot exhaustive and \milp scale poorly because of expensive motion planning.
Interestingly, motion planning infeasibility reduces the size of the exhaustive search tree.
The solution costs \textit{(middle)} substantiate benefits of the use of two arms. The computation times \textit{(bottom)} again show the scalability of \algo, even compared to random split.
% In terms of cost. MILP scales to more objects but the computational overhead is more than \algo. Dual-arm solutions are significantly better than single arm.

@@

The problem of optimizing the assignment of arms to objects will be affected by the reachability. Expectedly, the naive random split tends to erroneously assign unreachable objects to arms. The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, further highlights the benefits of dual-arm rearrangement.

@@

>>>>

\revisions{Note that we choose to focus on balanced problem instances where at least half of the objects are reachable to one of the robots. Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that requires no dual-arm coordination, while the proposed method remains unchanged.}

@@

\subsection{General Dexterous Manipulator} The second benchmark sets up two \kuka arms across a table with objects on it. The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose. \revisions{For the Kuka arms top-down reachability exists in an annular region between 40-70cm from the base of each robot. The robots were placed 1.1m apart. Experiments were performed on the largest rectangle that fitted within the intersection of the annular reachability regions.}

Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates. 
% The lazy iterative variants show the robust scalability. 
Random split performs the worst since it is unlikely to chance upon valid motion plans. Single shot exhaustive and \milp scale poorly because of expensive motion planning.
Interestingly, motion planning infeasibility reduces the size of the exhaustive search tree.
The solution costs \textit{(middle)} substantiate benefits of the use of two arms. The computation times \textit{(bottom)} again show the scalability of \algo, even compared to random split.
% In terms of cost. MILP scales to more objects but the computational overhead is more than \algo. Dual-arm solutions are significantly better than single arm.

@@

The problem of optimizing the assignment of arms to objects will be affected by the reachability. Expectedly, the naive random split tends to erroneously assign unreachable objects to arms. The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, further highlights the benefits of \dual-arm rearrangement.

@@

\revisions{\textit{Note on Heuristic Strategies: } 
	%Alternative simplified strategies exist for this problem domain. A significant complexity in the studied problem arises from the coordination of the arms, especially for general manipulators. Decoupled motion planning here with coordination of single-arm solutions is typically faster but loses guarantees of completeness. 
%	For the assignment of objects to arms fast heuristics can be designed to allocate the objects based some partitioning of the workspace. The focus of the current work is however on problems where the arms have to move and coordinate in common regions where such a partition might not exist, and decoupled solutions might not work.
	 It is possible that instead of the random baseline, some other heuristic might be used to allocate the objects to arms, like the proximity of objects to arms or some workspace partitioning. Such a deterministic, decoupled heuristic will make it faster to compute object-arm assignments than the proposed reasoning, but trade off the optimality bounds posited in this work. Given the object-to-arm assignments feasibility of the solution ultimately depends on coordinated motion planning. It should be noted that committing to a single choice of object assignments seriously affects success rates (especially in the Kuka benchmark). The success is only increased using our proposed lazy approach which takes into account such infeasibility and keeps reattempting other alternatives. A deterministic heuristic however will not offer alternative object-arm assignments and thus is incompatible with the improvements obtained from lazy evaluation. As such we leave the learning and incorporation of appropriate heuristics in this domain as future work and a motivation for practitioners.}
